---
title: "Produce 101 seasons 1 & 2 data analysis"
author: Olina Liang
date: October 19, 2017
output: #md_document
  ioslides_presentation:
    widescreen: true
    smaller: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, message=FALSE, echo = F)
#options(knitr.table.format = "html") 
```
# Produce 101
## Introduction
- Produce 101 is a korean survival reality show on Mnet. 
- It is a large-scale project in which the public (called 'national producers') "produces" a unit group by choosing 11 members among 101 trainees from over 50 entertainment companies.
- The show has 11 episodes.
- In the first two episodes, the trainees' are ranked by judges from A to E based on their perfromance which determines their position in the first trailor. And in each episode, their ranking are calculated by votings by viewers, the bottom ones are eliminated.
- There are different votings based on their performance in different tasks.
- Season 1 consist of all girls while season 2 is all boys.
- This project aims to explore which kind of trainees are more likely to debut.

## Packages
```{r, message=FALSE, echo = T}
library(readxl)
library(rvest)
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(stringr)
library(ggvis)
library(ggbio)
library(knitr)
library(kableExtra)
```

# Cleaning data
## Data
- Data from webpage (Wikipedia)
- https://en.wikipedia.org/wiki/List_of_Produce_101_contestants
- https://en.wikipedia.org/wiki/List_of_Produce_101_Season_2_contestants
- Korean TV show produce 101, seasons 1 and 2
- Tables for overall rank & performances for different tasks
```{r}
#get data from web
#s1
webpage1 <- read_html("https://en.wikipedia.org/wiki/List_of_Produce_101_contestants")
#table 1
tbls_s1 <- webpage1 %>%
  html_nodes("table")%>%
  .[1] %>%
  html_table(fill = TRUE)

#s2
webpage2 <- read_html("https://en.wikipedia.org/wiki/List_of_Produce_101_Season_2_contestants")
#table 1
tbls_s2 <- webpage2 %>%
  html_nodes("table")%>%
  .[1] %>%
  html_table(fill = T)
```

```{r, message=FALSE}
#s1
pd101_s1_ <- tbls_2s[[1]]
pd101_s1_$Company <- str_replace_all(pd101_s1_$Company, "[^[:ascii:]]", "") %>%
  str_replace_all("\\(.*\\)", "")
pd101_s1_$Name <- str_replace_all(pd101_s1_$Name, "[^[:ascii:]]", "") %>%
  str_replace_all("\\(.*\\)", "") 
pd101_s1_$Name <- gsub("[[:digit:]]", "", pd101_s1_$Name)
names(pd101_s1_) <-  make.names(names(pd101_s1_), unique = T)
pd101_s1_tbl1 <- 
  filter(pd101_s1_, Age>10&Age<50) %>%
mutate(age = type.convert(Age), 
       ranking = type.convert(Ranking),
       evaluation1 = type.convert(Judges.evaluation),
       evaluation1_num = as.numeric(evaluation1),
       evaluation2 = type.convert(Judges.evaluation.1),
       evaluation2_num = as.numeric(evaluation2), 
       ranking_ep1 = as.numeric(Ranking),
       ranking_ep2 = as.numeric(Ranking.1))
pd101_s1_tbl1 <- pd101_s1_tbl1 %>%
  mutate(Name = str_trim(Name))

#s2
tbl1 <- tbls_ls[[1]]

tbl1$Company <- str_replace_all(tbl1$Company, "[^[:ascii:]]", "") %>%
  str_replace_all("\\(.*\\)", "")
tbl1$Name <- str_replace_all(tbl1$Name, "[^[:ascii:]]", "") %>%
  str_replace_all("\\(.*\\)", "") 
tbl1$Name <- gsub("[[:digit:]]", "", tbl1$Name)

names(tbl1) <-  make.names(names(tbl1), unique = T)

table_1 <- 
  filter(tbl1, Age>10&Age<50)

pd101_s2_tbl1 <- 
mutate(table_1, age = type.convert(table_1$Age), 
       ranking = type.convert(table_1$Ranking),
       evaluation1 = type.convert(Judges.evaluation),
       evaluation1_num = as.numeric(evaluation1),
       evaluation2 = type.convert(Judges.evaluation.1),
       evaluation2_num = as.numeric(evaluation2), 
       ranking_ep1 = as.numeric(Ranking),
       ranking_ep2 = as.numeric(Ranking.1))
pd101_s2_tbl1 <- pd101_s2_tbl1 %>%
  mutate(Name = str_trim(Name))

#table 2
tbl2 <- webpage2 %>%
  html_nodes("table")%>%
  .[2] %>%
  html_table(fill = TRUE)
```

## Data table
- Cleaned name of trainees
- Changed type of age and ranking to integers
- Assigned evaluation numeric values

## Data table season 1

```{r}
kable(pd101_s1_tbl1, "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive")) %>%
  scroll_box(width = "90%", height = "300px")
```

## Data table season 1
```{r}
kable(pd101_s2_tbl1, "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "responsive")) %>%
  scroll_box(width = "90%", height = "300px")
```


# Analysis
# Age of trainees
## Age distribution table
- Not random
```{r}
pd101_s1_tbl1 <- pd101_s1_tbl1 %>%
  mutate(final_ranking = as.numeric(Ranking.12))

pd101_s2_tbl1 <- pd101_s2_tbl1 %>%
  mutate(final_ranking = as.numeric(Ranking.12))

pd101_s1_tbl1 %>%
  count(cut_width(age, 5))

pd101_s2_tbl1 %>%
  count(cut_width(age, 5))
```
## Age bar plot season 1
- Most trainees around 20 years old.
```{r}
ggplot(data = pd101_s1_tbl1) +
 geom_bar(mapping = aes (x = age), color = "palevioletred1")
```

## Age bar plot season 2
- Most trainees around 23 years old.
```{r}
ggplot(data = pd101_s2_tbl1) +
 geom_bar(mapping = aes (x = age), color = "steelblue2")
```

## Age frequncy comparison
- Age of female trainees are generally younger than male trainees.
```{r}
#ggplot(data = pd101_s1_tbl1) +
#geom_bar(mapping = aes (x = age))

#ggplot(data = pd101_s2_tbl1) +
#geom_bar(mapping = aes (x = age))

pd101_s1_tbl1$season <- "season 1"
pd101_s2_tbl1$season <- "season 2"

dd <- dplyr::bind_rows(pd101_s1_tbl1[, c("age", "season")],
              pd101_s2_tbl1[, c("age", "season")])

#dd

ggplot() +
  geom_freqpoly(data = dd, mapping = aes(x = age, color = season)) 


```

## Age and ranking season 1
- The ranking in first episode is more based on first impression while final ranking is based on viewers' holistic evaluation of a trainee.
- Lighter color represents ranking in first episode, darker represents ranking in last episode
- Left one cut by number, right one cut by age interval
- The younger trainees' ranking tend to increase while the older trainees' ranking tend to decrease.
```{r, warning=F}
t1 <- ggplot(data = pd101_s1_tbl1) + 
  geom_boxplot(mapping = aes(x = age, y = ranking, group = cut_number(age, 5)), alpha = 0.4, color = "palevioletred1") + 
  geom_boxplot(mapping = aes(x = age, y = final_ranking, group = cut_number(age, 5)),alpha = 0.3, color = "palevioletred4")

t2<- ggplot(data = pd101_s1_tbl1) + 
  geom_boxplot(mapping = aes(x = age, y = ranking, group = cut_width(age, 3)), alpha = 0.4, color = "palevioletred1") + 
  geom_boxplot(mapping = aes(x = age, y = final_ranking, group = cut_width(age, 3)),alpha = 0.3, color = "palevioletred4")

grid.arrange(t1, t2, ncol=2)
```
## Age and ranking season 1
- The ranking in first episode is more based on first impression while final ranking is based on viewers' holistic evaluation of a trainee.
- Lighter color represents ranking in first episode, darker represents ranking in last episode
- Left one cut by number, right one cut by age interval
- No patterns
```{r}
t1 <- ggplot(data = pd101_s2_tbl1) + 
  geom_boxplot(mapping = aes(x = age, y = ranking, group = cut_number(age, 5)), alpha = 0.4, color = "steelblue2") + 
  geom_boxplot(mapping = aes(x = age, y = final_ranking, group = cut_number(age, 5)),alpha = 0.3, color = "steelblue4")

t2<- ggplot(data = pd101_s2_tbl1) + 
  geom_boxplot(mapping = aes(x = age, y = ranking, group = cut_width(age, 3)), alpha = 0.4, color = "steelblue2") + 
  geom_boxplot(mapping = aes(x = age, y = final_ranking, group = cut_width(age, 3)),alpha = 0.3, color = "steelblue4")

grid.arrange(t1, t2, ncol=2)
```

## Age box plot and ranking comparison
- Cut by number on the left, cut by age interval on the right.
- Girls around 20 has best ranking, while younger boys (~17) have best ranking.
```{r, warning=F}
t1 <- ggplot(data = pd101_s1_tbl1) + 
  geom_boxplot(mapping = aes(x = age, y = ranking, group = cut_number(age, 5)), alpha = 0.4, color = "palevioletred1") + 
  geom_boxplot(mapping = aes(x = age, y = final_ranking, group = cut_number(age, 5)),alpha = 0.3, color = "palevioletred4")

t2<- ggplot(data = pd101_s1_tbl1) + 
  geom_boxplot(mapping = aes(x = age, y = ranking, group = cut_width(age, 3)), alpha = 0.4, color = "palevioletred1") + 
  geom_boxplot(mapping = aes(x = age, y = final_ranking, group = cut_width(age, 3)),alpha = 0.3, color = "palevioletred4")

t3 <- ggplot(data = pd101_s2_tbl1) + 
  geom_boxplot(mapping = aes(x = age, y = ranking, group = cut_number(age, 5)), alpha = 0.4, color = "steelblue2") + 
  geom_boxplot(mapping = aes(x = age, y = final_ranking, group = cut_number(age, 5)),alpha = 0.3, color = "steelblue4")

t4 <- ggplot(data = pd101_s2_tbl1) + 
  geom_boxplot(mapping = aes(x = age, y = ranking, group = cut_width(age, 3)), alpha = 0.4, color = "steelblue2") + 
  geom_boxplot(mapping = aes(x = age, y = final_ranking, group = cut_width(age, 3)),alpha = 0.3, color = "steelblue4")

grid.arrange(t1, t2, t3, t4, ncol=2)
```


# Judge evaluation
## Distribution in season 1
- Most people in F, least in A
- More people in A for the second time
```{r}
t1 <- ggplot(data = pd101_s1_tbl1) +
 geom_bar(mapping = aes (x = Judges.evaluation), color = "palevioletred1")

t2 <- pd101_s1_tbl1 %>%
  filter(Judges.evaluation.1 == "A"|Judges.evaluation.1 == "B"|Judges.evaluation.1 == "C"|Judges.evaluation.1 == "D"|Judges.evaluation.1 == "F") %>%
ggplot() +
 geom_bar(mapping = aes (x = Judges.evaluation.1), color = "palevioletred1")

grid.arrange(t1, t2, ncol=2)
```

## Distribution in season 2
- Evaluation increased and least in A class. Probably planned by the show.
```{r}
t1 <- ggplot(data = pd101_s2_tbl1) +
 geom_bar(mapping = aes (x = Judges.evaluation), color = "steelblue2")

t2 <- ggplot(data = pd101_s2_tbl1) +
 geom_bar(mapping = aes (x = Judges.evaluation.1), color = "steelblue2")

grid.arrange(t1, t2, ncol=2)
```

##Ranking and judge evaluation for season 1
- Evaluation for top 20
- Most A's
```{r}
pd101_s1_tbl1 %>%
  filter(Ranking.11>0) %>%
  ggplot() +
 geom_bar(mapping = aes (x = Judges.evaluation.1), color = "palevioletred1")
```

##Ranking and judge evaluation for season 2
- Evaluation for top 20
- Not really depend on evaluation
```{r}
pd101_s2_tbl1 %>%
  filter(Ranking.11>0) %>%
  ggplot() +
 geom_bar(mapping = aes (x = Judges.evaluation.1), color = "steelblue2")
```

## Evaluation and traning time for season 2
- People with high evaluation tend to have longer training time
```{r}
pd101_s1_height <- read_csv("pd101_heights_s1.csv")
pd101_s2_height <- read_csv("pd101_heights.csv")

pd101_s1_tbl1 <- pd101_s1_tbl1 %>% 
  full_join(pd101_s1_height, by = "Name") %>%
  filter(is.na(ranking_ep1) == F)

pd101_s2_tbl1 <- pd101_s2_tbl1 %>% 
  full_join(pd101_s2_height, by = "Name") %>%
  filter(is.na(ranking_ep1) == F)

pd101_s1_tbl1 <- pd101_s1_tbl1 %>%
  mutate(Training_time = Training_time_month + Training_time_years*12)

pd101_s2_tbl1 <- pd101_s2_tbl1 %>%
  mutate(Training_time = Training_time_month + Training_time_years*12)

ggplot(pd101_s1_tbl1) + 
geom_boxplot(aes(x = evaluation1_num, y = Training_time, 
                 group = cut_width(evaluation1_num, 1)), color = "palevioletred1")

ggplot(pd101_s2_tbl1) + 
geom_boxplot(aes(x = evaluation1_num, y = Training_time, 
                 group = cut_width(evaluation1_num, 1)), color = "steelblue2")
```


## Rankings and judge evaluation
- A(best) = 1, F(worst) = 5
```{r}
pd101_s1_rk <- pd101_s1_tbl1 %>% 
  mutate(evaluation_df = evaluation2_num - evaluation1_num) %>%
  mutate(ranking_df = ranking_ep1 - ranking_ep2)

pd101_s2_rk <- pd101_s2_tbl1 %>% 
  mutate(evaluation_df = evaluation2_num - evaluation1_num) %>%
  mutate(ranking_df = ranking_ep1 - ranking_ep2)

ggplot() +
  geom_point(pd101_s1_rk, mapping = aes(x = evaluation_df, y = ranking_df), color = "red") 

ggplot() +
  geom_point(pd101_s2_rk, mapping = aes(x = evaluation_df, y = ranking_df), color = "blue")


ggplot(data = pd101_s1_rk, aes(x = evaluation_df, y = ranking_df)) + 
  geom_boxplot(color = "red", aes(group = cut_width(evaluation_df, 1)))

ggplot(data = pd101_s2_rk, aes(x = evaluation_df, y = ranking_df)) + 
  geom_boxplot(color = "blue", aes(group = cut_width(evaluation_df, 1)))
```


## Group by companies
```{r}
trainee_company_s1 <-
  group_by(pd101_s1_tbl1, Company) %>%
  summarise(ranking = mean(ranking), 
            n_of_trainee = n(),
            evaluation = mean(evaluation1_num)) %>%
  arrange(desc(n_of_trainee))
kable(trainee_company_s1,"html") %>%
  scroll_box(width = "90%", height = "200px")

trainee_company_s2 <-
  group_by(pd101_s2_tbl1, Company) %>%
  summarise(ranking = mean(ranking, na.rm = T), 
            n_of_trainee = n(),
            evaluation = mean(evaluation1_num)) %>%
  arrange(desc(n_of_trainee))
kable(trainee_company_s2,"html") %>%
  scroll_box(width = "90%", height = "200px")
```

## Company rankings and judge evaluation
```{r}
trainee_company_s1_top_e1 <-
  group_by(pd101_s1_tbl1, Company) %>%
  summarise(ranking = mean(ranking_ep1, na.rm = T),
            n_of_trainee = n(), 
            evaluation = mean(evaluation1_num)) %>%
  arrange(desc(n_of_trainee)) %>%
  filter(n_of_trainee >= 3)

trainee_company_s1_top_e2 <-
  group_by(pd101_s1_tbl1, Company) %>%
  summarise(ranking = mean(ranking_ep2, na.rm = T),
            n_of_trainee = n(), 
            evaluation = mean(evaluation2_num)) %>%
  arrange(desc(n_of_trainee)) %>%
  filter(n_of_trainee >= 3)
#trainee_company_s1_top_e1

trainee_company_s2_top_e1 <-
  group_by(pd101_s2_tbl1, Company) %>%
  summarise(ranking = mean(ranking_ep1, na.rm = T), 
            n_of_trainee = n(),
            evaluation = mean(evaluation1_num)) %>%
  arrange(desc(n_of_trainee)) %>%
  filter(n_of_trainee >= 3)

trainee_company_s2_top_e2 <-
  group_by(pd101_s2_tbl1, Company) %>%
  summarise(ranking = mean(ranking_ep2, na.rm = T),
            n_of_trainee = n(), 
            evaluation = mean(evaluation2_num)) %>%
  arrange(desc(n_of_trainee)) %>%
  filter(n_of_trainee >= 3)
#trainee_company_s2_top

#ep1 ranking vs. evaluation
ep1 <- ggplot() +
  geom_point(trainee_company_s1_top_e1, mapping = aes(x = ranking, y = Company, color = evaluation), size = 4) +
  geom_point(trainee_company_s2_top_e1, mapping = aes(x = ranking, y = Company, color = evaluation), size = 4, shape = 17)
ep1

#ep2 ranking vs. evaluation
ep2 <- ggplot() +
  geom_point(trainee_company_s1_top_e2, mapping = aes(x = ranking, y = Company, color = evaluation), size = 4)+
  geom_point(trainee_company_s2_top_e2, mapping = aes(x = ranking, y = Company, color = evaluation), size = 4, shape = 17)
ep2

tracks(Episode1 = ep1, Episode2 = ep2, main = "Ranking vs. Evaluation")
```

## Company rankings and judge evaluation
```{r}
trainee_company_s1_top_individuals <-
  group_by(pd101_s1_tbl1, Company) %>%
  mutate(n_of_trainee = n()) %>%
  filter(n_of_trainee >= 5) %>%
  ungroup()

#trainee_company_s1_top_individuals

trainee_company_s2_top_individuals <-
  group_by(pd101_s2_tbl1, Company) %>%
  mutate(n_of_trainee = n()) %>%
  filter(n_of_trainee >= 5) %>%
  ungroup()

#trainee_company_s2_top_individuals

ggplot() +
  geom_point(trainee_company_s1_top_individuals, mapping = aes(x = ranking, y = evaluation1_num, color = Company)) +
  geom_point(trainee_company_s2_top_individuals, mapping = aes(x = ranking, y = evaluation1_num, color = Company), shape = 17)
```

##Height
```{r}
ggplot(data = pd101_s1_tbl1, mapping = aes(x = Height)) +
  geom_histogram(bins = 5, color = "red") 

ggplot(data = pd101_s2_tbl1, mapping = aes(x = Height)) +
  geom_histogram(bins = 5, color = "blue") 
  #geom_density()
```

##Height and ranking
```{r}
ggplot(data = pd101_s2_tbl1, aes(x = Height, y = ranking)) +
  geom_point(color = "blue")

ggplot(data = pd101_s2_tbl1, aes(x = Height, y = ranking)) + 
  geom_boxplot(color = "blue", aes(group = cut_width(Height, 5, boundary = 165)))

ggplot(data = pd101_s2_tbl1, aes(x = Height, y = ranking)) + 
  geom_boxplot(color = "blue", aes(group = cut_number(Height, 5, boundary = 165)))
```

##Height, age and ranking
```{r}
ggplot(pd101_s2_tbl1, aes(x = Height, y = Age)) +
  geom_tile(mapping = aes(fill = ranking_ep1))
```

##Training period
```{r}
ggplot(data = pd101_s2_tbl1, mapping = aes(x = Training_time)) +
  geom_histogram(bins = 5, color = "blue") 

ggplot(data = pd101_s2_tbl1, mapping = aes(x = Training_time)) +
  geom_histogram(bins = 10, color = "blue") 
```

##Training period and ranking
```{r}
ggplot(data = pd101_s2_tbl1, mapping = aes(x = Training_time, y = ranking)) +
  geom_point(color = "blue") 

ggplot(data = pd101_s2_tbl1, mapping = aes(x = Training_time, y = ranking)) +
  geom_boxplot(color = "blue", aes(group = cut_number(Training_time, 10)))

ggplot(data = pd101_s2_tbl1, mapping = aes(x = Training_time, y = ranking)) +
  geom_boxplot(color = "blue", aes(group = cut_width(Training_time, 30, boundary = 0)))
```

##When did they start training
```{r}
pd101_s2_tbl1 <- pd101_s2_tbl1 %>%
  mutate(start_age = age - Training_time/12)

ggplot(data = pd101_s2_tbl1, mapping = aes(x = start_age)) +
  geom_histogram(bins = 10, color = "blue") 
```

##Age when training started and ranking
###Generally people who started earlier have a higher rank
```{r}
ggplot(data = pd101_s2_tbl1, mapping = aes(x = start_age, y = ranking)) +
  geom_point(color = "blue") 

ggplot(data = pd101_s2_tbl1, mapping = aes(x =start_age, y = ranking)) +
  geom_boxplot(color = "blue", aes(group = cut_number(start_age, 5)))

ggplot(data = pd101_s2_tbl1, mapping = aes(x = start_age, y = ranking)) +
  geom_boxplot(color = "blue", aes(group = cut_width(start_age, 5, boundary = 0)))
```
##Weight
```{r}
ggplot(data = pd101_s2_tbl1, mapping = aes(Weight)) +
  geom_histogram(bins = 10, color = "blue") 

ggplot(data = pd101_s2_tbl1, mapping = aes(x = Weight, y = Height)) +
  geom_jitter(color = "blue") 
```

#if there's a big change between the ranking in first episode and last
#female heights
#if company influences ranking: both female and male ranking
#if training time influences ranking
#if when they started training influences ranking

#ggplotly


#slides should be self explanatory
#put web link for produce 101, why explain
#https://www.wattpad.com/209127413-produce-101-profiles-season-1-018-zhou-jieqiong-%E2%98%86


